An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-09-22 paper.tex
Tidy RQs for §5.3

@@

\pb{RQ1: are higher levels of the hierarchy growing or becoming more
centralised? are they associated with an increased domination of the
conversation?}

@@

@@

\pb{RQ2: What is the association between the organisation hierarchy and
general communication patterns?}

@@

@@

\pb{RQ3: How do people with differing roles communicate with each other?
Does information flow ``up" or ``down" the hierarchy?}

@@

@@

\pb{RQ4: What is the impact that individuals have on their direct contacts'
activity over time? How does this vary across hierarchy level?}

>>>>

% RQ1: Are higher levels of the hierarchy growing or becoming more
% centralised? Are they associated with an increased domination of
% the conversation?

@@

@@

% RQ2: What is the association between the organisation hierarchy and
% general communication patterns?

@@

@@

% RQ3: How do people with differing roles communicate with each other?
% Does information flow ``up" or ``down" the hierarchy?

@@

@@

% RQ4: What is the impact that individuals have on their direct contacts'
% activity over time? How does this vary across hierarchy level?

@@
